An open reproducible framework for the study of the iterated prisoner's dilemma

### 2015-10-16 tex/paper.tex
Reorganisation and first draft of intro.

\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{booktabs}

@@

\begin{itemize}
    \item Describe library,
    \item Perhaps include image like:
        http://vknight.org/Talks/2015-10-12-Evolutionary-mathematics/static/outline_of_library.svg
        (am playing with https://pycallgraph.readthedocs.org/en/master/)
    \item Show code to create basic tournament
    \item Show code for a strategy
    \item Show process to contribute strategy
\end{itemize}

>>>>

\usepackage{amsmath}  % Basic
\usepackage{hyperref}  % Links etc
\usepackage{booktabs}  % Better tables
\usepackage{listings}  % Code
\usepackage{graphicx}  % Images

@@

The library is written in Python (\url{http://www.python.org/}) which is a
popular language in the academic community with libraries developed for:

\begin{itemize}
    \item Machine learning (\url{http://scikit-learn.org/});
    \item Visualisation (\url{http://matplotlib.org/});
    \item Mathematics (\url{http://www.sagemath.org/}).
\end{itemize}

In \cite{Isaac2008} Python is described as an appropriate language for the
reproduction of Iterated Prisoner's dilemma tournaments due to it's object
oriented nature and readability.

The library itself is available at
\url{https://github.com/Axelrod-Python/Axelrod}. This is a hosted git repository
which. Git is a popular version control system which is one of the recommended
aspects of reproducible research \cite{Crick2014a, Sandve2013}.

Figure~\ref{fig:demo_tournament_commands} shows a very simple example of using
the library to create a basic tournament with the graphical output shown in
Figure~\ref{fig:demo_tournament}.

\begin{figure}[!hbtp]
    \begin{lstlisting}[frame=single]
>>> import axelrod
>>> strategies = [s() for s in axelrod.demo_strategies])
>>> tournament = axelrod.Tournament(strategies)
>>> results = tournament.play()
>>> plot = axelrod.Plot(results)
>>> plot.boxplot()
    \end{lstlisting}
    \caption{A simple set of commands to create a demonstration tournament. The
        output is shown in Figure~\ref{fig:demo_tournament}.}
    \label{fig:demo_tournament_commands}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.8\textwidth]{../img/demo_tournament.pdf}
    \caption{The results from a simple tournament.}
    \label{fig:demo_tournament}
\end{figure}

This just shows the very basic utilisation of the library and further details
can be found at the online documentation:
\url{http://axelrod.readthedocs.org}. Some further implemented capabilities include:

\begin{itemize}
    \item Noisy tournaments;
    \item Ecological tournaments;
    \item Full tournament history.
\end{itemize}

As stated in Section~\ref{sec:introduction} one of the main goals of the library
is to allow for the easy contribution of strategies. To do this requires the
writing of a simple python class (which can inherit from other predefined
classes). Full contribution guidelines can be found in the documentation.
Figures~\ref{fig:grudger} and~\ref{fig:grudger_test} show the source code for
the Grudger strategy as well as it's corresponding test.

\begin{figure}[!hbtp]
    \begin{lstlisting}[frame=single]
class Grudger(Player):
    """A player starts by cooperating however will defect if
       at any point the opponent has defected."""

    name = 'Grudger'
    classifier = {
        'memory_depth': float('inf'),  # Long memory
        'stochastic': False,
        'inspects_source': False,
        'manipulates_source': False,
        'manipulates_state': False
    }

    def strategy(self, opponent):
        """Begins by playing C, then plays D for the remaining
           rounds if the opponent ever plays D."""
        if opponent.defections:
            return D
        return C
    \end{lstlisting}
    \caption{Source code for the Grudger strategy.}
    \label{fig:grudger}
\end{figure}

\begin{figure}[!hbtp]
    \begin{lstlisting}[frame=single]
class TestGrudger(TestPlayer):

    name = "Grudger"
    player = axelrod.Grudger
    expected_classifier = {
        'memory_depth': float('inf'),  # Long memory
        'stochastic': False,
        'inspects_source': False,
        'manipulates_source': False,
        'manipulates_state': False
    }

    def test_initial_strategy(self):
        """
        Starts by cooperating
        """
        self.first_play_test(C)

    def test_strategy(self):
        """
        If opponent defects at any point then the player will defect forever
        """
        self.responses_test([C, D, D, D], [C, C, C, C], [C])
        self.responses_test([C, C, D, D, D], [C, D, C, C, C], [D])
    \end{lstlisting}
    \caption{Source code for the Grudger strategy.}
    \label{fig:grudger}
\end{figure}

You can see an overview of some of the source code in Figure~\ref{fig:overview}.

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.8\textwidth]{../img/outline_of_library.pdf}
    \caption{An overview of the source code.}
    \label{fig:overview}
\end{figure}

To date the library has had contributions from 19 contributors from a variety of
backgrounds. These contributions have both been in terms of strategies (one
strategy is the creation of an undergraduate mathematics student with little
prior knowledge of programming) as well as the architecture of the library
itself.

Before discussing the novel insights obtained from the study of this library in
Section~\ref{sec:new-strategies-and-implications} an overview of some
tournaments that have been reproduced will be given in
Section~\ref{sec:reproducing-previous-tournaments}.
